Capstone Movielens Report

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Helper functions review: Model regularization process.

::: {.noteblock data-latex=""}
This function is also intended to be passed as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
:::
:::

>>>>

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
:::
:::
